%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Solutions Architect Intern} % Job title 
{Amazon Web Services (AWS)} % Organization
{Toronto, ON} % Location
{April 2025 – Present} % Date(s)%
{ % Description(s) of tasks/responsibilities
  \begin{cvitems}
    \item {Designed and supported scalable, secure, and cost-optimized AWS architectures for customer workloads, aligning cloud solutions with technical and business objectives.}
    \item {Built interactive dashboards using Amazon QuickSight, integrating datasets from Amazon S3 and AWS Athena to enable near real-time analytics for customers.}
    \item {Participated in technical deep dives and architecture reviews with customers, identifying opportunities to improve performance and reliability using services such as EC2, RDS, Lambda, and CloudFront.}
    \item {Translated stakeholder feedback into clear technical requirements for product teams, contributing to customer-centric service improvements.}
    \item {Conducted hands-on walkthroughs and labs to upskill customer engineering teams on IAM, serverless architecture, VPC networking, and analytics services.}
    \item {Produced reusable reference architectures, knowledge articles, and automation scripts to accelerate cloud adoption and onboarding for customers.}
    \item {Shadowed customer discovery sessions and contributed to cloud solutioning by asking strategic questions that uncovered underlying technical challenges.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
  {PowerApps and Power BI Developer and Technical Support Analyst} % Job title 
  {Shared Services Canada (SSC)} % Organization
  {Ottawa, Canada (Remote)} % Location
  {Jan. 2023 - Sept. 2024} % Date(s)%
  { % Description(s) of tasks/responsibilities
    \begin{cvitems}
      \item {Enhanced transparency and accountability, reducing unresolved issues by 25\%, by implementing a centralized tracking system built with PowerApps, integrating advanced search using business logic rules, and automating reminders for critical deadlines via Power Automate.}
      \item {Reduced manual effort and communication delays by enabling intake and project coordinator teams to electronically track BR progress through an automated checklist and exception evaluation, accelerating closure processes and improving decision-making.}
      \item {Increased adoption of a centralized tracking system by 30\% through the creation of over 10 comprehensive user guides, infographics, and organizational growth visuals, clarifying system benefits and easing integration for stakeholders.}
      \item {Resolved critical WCAG compliance issues, such as fixing tab order for screen readers and adding a column for environment names to enhance usability for assistive technology users, improving inclusivity across the platform.}
      \item {Developed a Power Automate flow to standardize and process over 250 monthly business request emails, categorizing them by attributes like client and environment type using hash tables, improving assignment accuracy and reducing intake team workload.}
      \item {Leveraged Excel features like VLOOKUP to analyze historical BR data, identifying trends in milestones such as CRQ dates and delays, providing actionable insights to optimize processes and improve planning.}
      \item {Designed and integrated over 10 UML class diagrams into the business architecture document, simplifying system understanding for new hires and stakeholders and facilitating collaboration during feature development.}
      \item {Developed a bilingual, searchable Power BI glossary containing over 200 terms, providing a single source of truth that streamlined onboarding, improved team alignment, and reduced reliance on live instruction.}
      \item {Produced 20 bilingual software training videos within two months, onboarding dozens of executives and Linux/Unix administration teams, increasing efficiency and reducing miscommunication through accessible, consistent resources.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {DotNetNuke C\# Web Developer} % Job title
  {Toronto District School Board (TDSB)} % Organization
  {Toronto, Ontario} % Location
  {May 2021 - Dec. 2022} % Date(s)%
  { % Description(s) of tasks/responsibilities
    \begin{cvitems}
      \item {Enhanced the public-facing website's AODA compliance by using website crawlers like SiteImprove and custom scripts to scan HTML attributes, improving accessibility across the board's online presence.}
      \item {Improved user navigation and experience by enhancing the sports event web application, introducing filters to sort events by gender and type (e.g., boys' basketball, girls' swimming).}
      \item {Remediated and quality-tested over 100 web pages, 50 school websites, and 20 web modules under time pressure, ensuring AODA compliance by adhering to WCAG standards.}
      \item {Consulted with over 20 school principals and marketing officers to design and update public site webpages and school sites, improving website design and content.}
      \item {Deployed and tested the staff login page used across the entire school board under a tight deadline, delivering critical functionality.}
    \end{cvitems}
  }

%---------------------------------------------------------

\end{cventries}
