%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
\cvproject
{Spam Detector (Personal Project) - Java Developer} % Organization
{} % Job title
{}
{}
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Constructed a web application using a probabilistic model to predict spam likelihood of emails, trained on a comprehensive email dataset.}
    \item {Achieved over 95\% accuracy by filtering out stop words and assigning higher weights to spam keywords, enhancing the model's precision.}
  \end{cvitems}
}
%---------------------------------------------------------
\cvproject
{MyFileBackPack (Home Lab) - AWS Developer} % Job title
{} % Organization
{}
{}
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed a scalable microservice API for handling text and image fragments, integrating authentication and authorization mechanisms using AWS Cognito and IAM, ensuring compliance with security standards.}
    \item {Implemented high-availability data storage solutions with AWS DynamoDB and S3, optimizing performance by designing efficient data models and access patterns, which reduced latency by 30\%.}
    \item {Deployed and managed the application using AWS ECS and Elastic Beanstalk, achieving efficient container orchestration and seamless integration with AWS services via the AWS SDK.}
  \end{cvitems}
}
\vspace{0.225cm} % Adds space equal to one line

%---------------------------------------------------------
\cvproject
{PantryPal (Hackathon Project) - Jr. solutions architect} % Job title
{} % Organization
{}
{}
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Achieved scalable and efficient deployment of the PantryPal application by leveraging Azure cloud services—including Azure Static Web Apps—and implementing CI/CD pipelines with GitHub workflows across DEV, TEST, and PROD environments, resulting in seamless integration, collaboration and faster deployment cycles.}
    \item {Enhanced client understanding and confidence by developing a comprehensive cloud architecture document, effectively communicating the application's technical design and deployment strategy.}
    \item {Implemented a NoSQL database using MongoDB with optimized collections, enabling efficient management of pantry items and recipes for users and chefs.}
  \end{cvitems}
}



%---------------------------------------------------------

\end{cventries}
