%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

    %---------------------------------------------------------
    Passionate full stack web developer with a focus on code-driven storytelling and conveying narratives about corporate app transformations and societal well-being. Proficient in developing and deploying cloud-based web applications to solve complex problems, engage users with captivating experiences, and drive business performance.

    Deployed a 200+ term Glossary report in Power BI, empowering employees under Linux Centralized Services department under Shared Services Canada to understand corporate applications and business processes used there better. Skilled in leveraging cloud services for business driven performance in e-commerce, file management, and social media applications.

    Strong advocate for women and the visually impaired in tech. Prefers a command line interface environment as a big fan of Vim, Linux, and macOS. Always trying to customize to find the most optimal environment. Interested in devising a better problem-solving method for challenging tasks, and learning new technologies and tools.
\end{cvparagraph}
